\documentclass[letterpaper,11pt]{article}

% Dependencies
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{fontawesome}
\usepackage{xcolor}

\input{glyphtounicode}

% Page Styling
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-0.8in}
\addtolength{\textheight}{1.6in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Define colors
\definecolor{headingblue}{RGB}{0, 51, 102}

% Set global text color to black for readability
\color{black}

% Section formatting
\titleformat{\section}{\vspace{-6pt}\scshape\raggedright\large\bfseries\color{headingblue}}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]
\titleformat{\subsection}{\vspace{-4pt}\scshape\raggedright\normalsize\bfseries\color{headingblue}}{\hspace{-.1in}}{0em}{}[\color{black}\vspace{-4pt}]

% Ensure ATS parsable
\pdfgentounicode=1

% Custom Commands
\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-3pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-3pt}\item
  \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-6pt}
}
\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{0.98\textwidth}{l@{\extracolsep{\fill}}r}
    \small\bfseries#1 & \small#2 \\
  \end{tabular*}\vspace{-6pt}
}
\newcommand{\resumeProjectHeadingWithLink}[3]{
  \item
  \begin{tabular*}{0.98\textwidth}{l@{\extracolsep{\fill}}r}
    \small\bfseries#1 (\href{#2}{#2}) & \small#3 \\
  \end{tabular*}\vspace{-6pt}
}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.1in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-6pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-6pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\begin{document}

% Heading
\begin{center}
  \textbf{\Huge \scshape Sujay Kumar} \\ \vspace{8pt}
  \small
  \vspace{2pt}
  \faGithub\ \href{https://github.com/Suuraw}{github.com/Suuraw} \quad
  \faLinkedin\ \href{https://linkedin.com/in/sujay-kumar-4b85b5252}{linkedin.com/in/sujay-kumar-4b85b5252} \quad
  \faEnvelope\ \href{mailto:sujayraw13@gmail.com}{sujayraw13@gmail.com} \quad
  \faPhone\ 7750015353
\end{center}
\vspace{-8pt}

% Summary
\section{Summary}
\vspace{4pt}
\resumeSubHeadingListStart
\item{Computer Science student focused on containerization, automation, and Kubernetes for scalable web solutions. Passionate about DevOps and cloud-native workflows; write technical blogs at \href{https://sujay.is-a.dev/blog}{\textcolor{blue}{\textbf{\textit{sujay.is-a.dev/blog}}}}.}
\resumeSubHeadingListEnd

% Education
\section{Education}
\vspace{4pt}
\resumeSubHeadingListStart
  \resumeSubheading{KIIT University}{Bhubaneswar, Odisha}{B.Tech, Computer Science and Engineering}{Expected Sep 2026, CGPA: 8.11/10}
\resumeSubHeadingListEnd

% Skills
\section{Skills}
\vspace{4pt}
\resumeSubHeadingListStart
  \item{
    \textbf{Programming Languages}: C, Java, JavaScript, TypeScript, Python \\ \vspace{2pt}
    \textbf{Web Technologies}: HTML5, CSS3, Tailwind CSS, React.js, Next.js, Node.js, Express.js, FastAPI, RESTful APIs \\ \vspace{2pt}
    \textbf{Databases \& Tools}: MongoDB, PostgreSQL, Firebase, Supabase, Prisma ORM, Postman \\ \vspace{2pt}
    \textbf{DevOps \& Cloud}: Git, GitHub, GitHub Actions, Google Cloud Platform, Cloudflare, Docker, AWS - EC2
  }
\resumeSubHeadingListEnd

% Experience
\section{Professional Experience}
\vspace{4pt}
\resumeSubHeadingListStart
  \resumeProjectHeading{\textbf{IIT Kharagpur} $|$ \emph{Research Collaborator}}{April 2025 -- Jun 2025}
  \resumeItemListStart
    \resumeItem{Collaborated with PhD students to develop a proxy index for measuring renewable energy market trends by creating a data pipeline.}
    \resumeItem{Utilized generative AI to create signaling keywords, integrated into a data pipeline for scraping the Scopus database, saved results to Excel, and visualized market trends.}
  \resumeItemListEnd

  \resumeProjectHeading{\textbf{KIIT E-Cell} $|$ \emph{Full Stack Developer}}{Sep 2024 -- Present}
  \resumeItemListStart
\resumeItem{Served as Full Stack Developer and Built a course dashboard using the MERN Stack and integrated Google Sheets API}
\resumeItem{Led the design and deployment of the organization's official website to improve outreach and digital presence.}
\resumeItem{Organized and managed an internal hackathon, overseeing the event's planning, logistics, and execution.}

  \resumeItemListEnd

  \resumeProjectHeading{\textbf{AGT Pvt Ltd} $|$ \emph{Full Stack Developer}}{Dec 2024 -- April 2025}
  \resumeItemListStart
    \resumeItem{Developed responsive UI components for photonBoxx, improving mobile responsiveness. \href{https://sujays-organization-1.gitbook.io/photonboxx-contribution/}{Contribution Link}}
    \resumeItem{Resolved critical UI bugs, boosting application uptime and enhancing user satisfaction.}
    \resumeItem{Streamlined CRUD operations for HobbyCue admin routes, increasing backend efficiency. \href{https://sujays-organization-1.gitbook.io/untitled/}{Contribution Link}}
  \resumeItemListEnd
\resumeSubHeadingListEnd

% Projects
\section{Key Projects}
\resumeSubHeadingListStart
  \resumeProjectHeadingWithLink{\textbf{ApplySmart}}{https://www.applysmart.me} {Next.js, Express, Prisma, MongoDB, AWS, Whisper, OpenAI API $|$ 2025}
  \resumeItemListStart
  \resumeItem{Built a career support platform to streamline job preparation for college students by offering AI-powered resume analysis, job application automation, and mock interview simulations.}
  \resumeItem{Developed an ATS scoring and resume analysis tool with chatbot suggestions to enhance resume alignment with job roles.}
  \resumeItem{Automated job application form-filling by generating pre-filled form replicas, along with custom cover letters and job-resume comparison insights.Currently,building our own Speech to Text model.}
  % \resumeItem{Integrated OpenAI API and Whisper-based Speech-to-Text/Text-to-Speech models to simulate mock interviews with dynamically generated questions.}
  % \resumeItem{Reduced resume rejection by improving alignment with job requirements and enhancing student interview readiness.}
  \resumeItemListEnd

  \resumeProjectHeadingWithLink{\textbf{Watch2Learn}}{https://www.watch2learn.app}{Next.js , FastAPI , Python , Docker $|$ 2025}
  \resumeItemListStart
  \resumeItem{Developed a YouTube-based study tool that extracts and summarizes transcripts using generative AI for detailed and concise learning.}
  \resumeItem{Solved the problem of vague incomplete video summarization by implementing a markdown-powered formatting engine.}
  \resumeItem{Enabled quiz generation from summaries to test retention, with persistent history to track user learning progress.}
  \resumeItemListEnd

  \resumeProjectHeadingWithLink{\textbf{E-Cell Cohort}}{https://ecohort.vercel.app}{React.js , Express , Sheet API , PostgreSQL $|$ 2024}
  \resumeItemListStart
  \resumeItem{Built a learning dashboard for onboarding KIIT E-Cell recruits with week-wise content, quizzes, and progress tracking.}
  \resumeItem{Solved manual leaderboard updates by integrating Google Sheets API for real-time quiz data and ranking display.}
  \resumeItem{Enhanced engagement through gamified elements and responsive UI deployed on Vercel with Tailwind styling.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

% Extracurricular Activities
\section{Extracurricular Achievements}
\resumeSubHeadingListStart
  \resumeProjectHeading{\textbf{National Basketball Player} $|$ \emph{Competitive Athlete}}{2018 -- Present}
  \resumeItemListStart
    \resumeItem{Represented state and college in national basketball tournaments, demonstrating leadership and teamwork under pressure.}
  \resumeItemListEnd

  \resumeProjectHeading{\textbf{Smart India Hackathon 2024} $|$ \emph{National-Level Competitor}}{2024}
  \resumeItemListStart
    \resumeItem{Secured Top 50 position among college teams, showcasing problem-solving and collaborative innovation.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}